---
title: "Time Series Plot for Kerala Ad Data"
author: "Suhaas Ramani"
date: "9/15/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---


Upon downloading the excel file that was provided I filtered the region_KL column and deleted the other regional areas on a new spreadsheet. 


I then needed to get rid of the timestamp that was placed with each ad creation. Hence why I created two columns, creation_date and creation_date_notime, respectively. For creation_date I used the "=SUBSTITUTE" function to delete the T character and replace it with a space. For the creation_date_notime column I used the "=INT" function to remove the timestamp and retrieve the column in just dates. 


After which I imported the excel file into R using the code below: 




```{r, echo=TRUE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readxl)
Kerala_ad <- read_excel("C:\\Users\\Suhaas Ramani\\Desktop\\R Research Project - Facebook Ads\\Filtered_Kerala_Ad_Data.xlsx")
```



After I imported the data, I filtered it to remove the NAs from the time variable, I then grouped the data by the time variable, and summarized the data to include a counts variable that contained the frequency for each date. This can be seen in the code below: 



```{r, echo=TRUE}
Kerala_ad <- Kerala_ad %>% 
  filter(!is.na(creation_date_notime)) %>%
  group_by(creation_date_notime) %>% 
  summarize(counts = n())
```



Finally I created the plot using the ggplot2 tool in R, where I placed time on the x-axis and counts on the y-axis. 



```{r, echo=TRUE}
Kerala_ad_plot <- ggplot(Kerala_ad, aes(x = creation_date_notime, y = counts)) + 
  geom_point() + 
  geom_line() + 
  geom_smooth() +
  geom_text(aes(label = counts), vjust = -0.5) + 
  xlab("Time") + 
  ggtitle("Time-Series Plot of Kerala Ad Data")

Kerala_ad_plot
```


As can be seen from this plot, the data shows a marked spike in ads from 7 to 788 on April 19th. 
